Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-11-01 Manuscript/manuscript.tex
Update methods text

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[height=\figheightsmall]{../img/ecc_pops/density_profiles_na-k-counterions_wat_phos_compar_purePOPS.pdf}
  \includegraphics[height=\figheightsmall]{../img/ecc_pops/density_profiles_na-k-counterions_wat_phos_compar_5PC-1PS.pdf} \\
  \includegraphics[height=\figheightsmall]{../img/ecc_pops/l17/density_profiles_na-k-counterions_wat_phos_compar_purePOPS_lipid17.pdf}
  \includegraphics[height=\figheightsmall]{../img/ecc_pops/l17/density_profiles_na-k-counterions_wat_phos_compar_5PC-1PS_lipid17.pdf}
  \caption{\label{fig:POPS-counterions-dens}
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} counterions along the membrane normal axis 
    for the negatively charged bilayers composed of only POPS (left) or POPC:POPS (5:1, right) 
    using ECC-lipids and ECC-ions (top) and Lipid17 (bottom).  }
\end{figure}

>>>>

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/density_profile_K-Na_counterions_compar_pure-ECC-POPS.pdf}
  \caption{\label{fig:POPS-counterions-dens}
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} counterions along the membrane normal axis 
    for the negatively charged POPS bilayers using ECC-lipids and ECC-ions.  }
\todo{Joe: TO BE UPDATED + results from PC:PS mixutres to be added.}
\end{figure}
